### 2021-06-29 README.Rmd
Bulleted lists in Readme

    *metadata.R creates the metadata rda file used for subsequent analyses.
    *phenotypes_2018.R creates the phenotypic data rda file used for analyses of 2018 data
    *phenotypes_2019.Rmd creates the phenotypic data rda file used for analyses of 2019 data. These plants differ from those in phenotypes_2018 - many plants that died were replaced by Blackwell cultivar clones, and any phenotypes measured on these clones were not included in downstream analyses.
    *Taxa.R creates the Taxa rda file used to tie sequence data to the 785 sequenced PLANT_IDs.

@@

    * Contains datasets as ".rds" files that are used in analyses (to produce results in the analysis/ folder). These files can be read into R using the `readRDS()` function.

@@

    * Data objects and draft figures created as part of the analysis of heritability (including variance components analysis, done in ASReml), genome-wide association (on phenotypic BLUPs, done using the switchgrassGWAS R package), and mash (on results from the univariate GWAS, done using the switchgrassGWAS R package). Generally, the code to replicate these analyses can be found in the R/ directory.

@@

    * Contains the majority of the code used in the manuscript (some additional code used to prepare data is in data-raw/.) 
    * Files that start with "Plots" were used to make manuscript figures
    * Files that start with "nohup" were used to run mash
    * Files that start with "Analysis" were used to generate files in the analysis/ folder. I tried to name these descriptively but there are a lot of them; please open a pull request if you want help locating specific code.

@@

    * Code and data objects needed to replicate the genetic mapping of flowering-related QTL in the pseudo-F2 cross.

@@

    * Contains completed drafts of a manuscript on the genetics of GxE in phenology in the switchgrass diversity panel.

>>>>

    - metadata.R creates the metadata rda file used for subsequent analyses.
    - phenotypes_2018.R creates the phenotypic data rda file used for analyses of 2018 data
    - phenotypes_2019.Rmd creates the phenotypic data rda file used for analyses of 2019 data. These plants differ from those in phenotypes_2018 - many plants that died were replaced by Blackwell cultivar clones, and any phenotypes measured on these clones were not included in downstream analyses.
    - Taxa.R creates the Taxa rda file used to tie sequence data to the 785 sequenced PLANT_IDs.

@@

    - Contains datasets as ".rds" files that are used in analyses (to produce results in the analysis/ folder). These files can be read into R using the `readRDS()` function.

@@

    - Data objects and draft figures created as part of the analysis of heritability (including variance components analysis, done in ASReml), genome-wide association (on phenotypic BLUPs, done using the switchgrassGWAS R package), and mash (on results from the univariate GWAS, done using the switchgrassGWAS R package). Generally, the code to replicate these analyses can be found in the R/ directory.

@@

    - Contains the majority of the code used in the manuscript (some additional code used to prepare data is in data-raw/.) 
    - Files that start with "Plots" were used to make manuscript figures
    - Files that start with "nohup" were used to run mash
    - Files that start with "Analysis" were used to generate files in the analysis/ folder. I tried to name these descriptively but there are a lot of them; please open a pull request if you want help locating specific code.

@@

    - Code and data objects needed to replicate the genetic mapping of flowering-related QTL in the pseudo-F2 cross.

@@

    - Contains completed drafts of a manuscript on the genetics of GxE in phenology in the switchgrass diversity panel.
